Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-22 Draft.Rmd
del margin

origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
  labs(title="PM2.5 Concentration by State", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") +
  theme(legend.position="none",strip.text.x = element_text(margin = margin()))
```

@@

# take top 20 important variables
import20 = import[1:20,]
```

@@

```{r Linear Regression}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ lat + lon + state)

>>>>

origin %>% ggplot(aes(x=value, fill=state)) + geom_histogram() + facet_wrap(~state) + 
  labs(title="PM2.5 Concentration by State", x="PM2.5 (mu g/m^3)", y="Frequency (Monitors)") +
  theme(legend.position="none")
```

@@

# take top 10 important variables
import10 = import[1:10,]
```

@@

```{r Linear Regression}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ )
